---
title: 'Class8:'
author: "Robertha Amezola"
date: "April 25, 2019"
output: github_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means clustering

Example of running the **kmeans()** function

```{r}
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))
plot(x)
```


To Do

-Use the kmeans() function setting k to 2 and nstart=20
-Inspect/print the results
>Q. How many points are in each cluster? 45
 
```{r}
km=kmeans(x, centers=2, nstart=20)
```
```{r}
km$cluster
```
 
```{r}
km$size
```

 
 
```{r}
km$centers
```
 
```{r}
plot(x, col=km$cluster)
points(km$centers, pch=18, col="blue", cex=3)
```
 
 

>Q. What ‘component’ of your result object details
 - cluster size?
 - cluster assignment/membership?
 - cluster center?
 
>Plot x colored by the kmeans cluster assignment and
 add cluster centers as blue points
 
```{r}
km <- kmeans(x, centers=2, nstart=20)

```
 
 
 ##Hierarchical Clustering example
 
 
 **hclust** function a distance matrix not the raw data as an input
 
```{r}
##distanc ematrix calculation
d <- dist(x)

##clustering
hc<-hclust(d)
plot(hc)

```
 
 # Create hierarchical cluster model: hc
hc <- hclust(dist(x))
# We can plot the results as a dendrogram
plot(hc)
>What do you notice? the grah is hard to read
>Does the dendrogram? every cluster (point) is then group into similar groupds
>make sense based on? yes but you have to understand that is backgrads 
>your knowledge of x
 
 
 ##drwas dendrogram
```{r}
plot(hc)
abline(h=6, col="red")

```
 
 
 ## # Cut into k grps can chang k
```{r}
cutree(hc, k=2)
```
 
 
## Step 1. Generate some example data for clustering 
```{r}
x <- rbind(
 matrix(rnorm(100, mean=0, sd = 0.3), ncol = 2), # c1
 matrix(rnorm(100, mean = 1, sd = 0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean = 1, sd = 0.3), # c3
 rnorm(50, mean = 0, sd = 0.3)), ncol = 2))
colnames(x) <- c("x", "y")
```
 
 ## Step 2. Plot the data without clustering
```{r}
plot(x)
```
 
 
 # Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)

```{r}
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```
 
>Use the dist(), hclust(), plot() and cutree()
 functions to return 2 and 3 clusters


 
```{r}
hc<- hclust(dist(x))
plot(hc)
abline(h=2, col="red")
abline(h=2.8, col="blue")
```
 
```{r}
gp2 <- cutree(hc, k=4)
gp3<-cutree(hc, k=5)
```

```{r}
gp2
```
 
```{r}
gp3
```

```{r}
plot(x, col=gp3)
```
 
```{r}
plot(x, col=gp2)
```
 
 
 ##PCA analysis
 **prcomp()**
```{r}
mydata <- read.csv("https://tinyurl.com/expression-CSV",
 row.names=1)
```
 ## tells you how many rows
 #100 genes
```{r}
nrow(mydata)
```
#how many experiment in colums
```{r}
ncol(mydata)
```
##colum name
```{r}
colnames(mydata)
```
 
 
```{r}
head(t (mydata))
```
 
```{r}
prcomp(t(mydata), scale=TRUE)
```
 
 
 #name pca
```{r}
pca <- prcomp(t(mydata), scale=TRUE)
```
 
#pca plot
```{r}
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2")
```

## variance capture per PC % in OC

```{r}
pca.var <- pca$sdev^2
pca.var.per <- round(pca.var/sum(pca.var)*100, 1) 

head(pca.var.per) 
```

```{r}
barplot(pca.var.per, main="Scree Plot",
 xlab="Principal Component", ylab="Percent Variation")
```


```{r}
colvec <- colnames(mydata)
colvec[grep("wt", colvec)] <- "red"
colvec[grep("ko", colvec)] <- "blue"

plot(pca$x[,1], pca$x[,2], col=colvec, pch=16,
 xlab=paste0("PC1 (", pca.var.per[1], "%)"),
 ylab=paste0("PC2 (", pca.var.per[2], "%)"))


 
```

#Hands on session 2


```{r}
ukfood<- read.csv("UK_foods.csv", row.names = 1)
```
 
```{r}
ncol(ukfood)
```
 

```{r}
dim(ukfood)


```



```{r}
rownames(ukfood) <- ukfood[,1]
ukfood <- ukfood[,-1]
head(ukfood)
```


```{r}
dim(ukfood)
```


```{r}
ukfood<- read.csv("UK_foods.csv", row.names=1)
head(ukfood)
```


```{r}
barplot(as.matrix(ukfood), beside=T, col=rainbow(nrow(ukfood)))
```

```{r}
barplot(as.matrix(ukfood),x, col=rainbow(10), pch=16)
```





```{r}
prcomp(ukfood)
pca<- prcomp(t(ukfood))
summary(pca)
```

#PCA

```{r}
plot(pca$x[,1], pca$x[,2], xlab="PC1", ylab="PC2", xlim=c(-270,500) )
text(pca$x[,1], pca$x[,2],colnames(ukfood))
```

```{r}
v <- round( pca$sdev^2/sum(pca$sdev^2) * 100 )
```
 ## values look for v %variation x PC
 
```{r}
barplot(v, xlab="Principal Component", ylab="Percent Variation")

```
 
 
