---
title: "class_13_hands_on"
author: "Robertha Amezola"
date: "May 14, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

genotypes in MXL 1000 Genome Project Data

Focused on MXN ancestry in LA,CA

what portion of MXN ancestry 
mxl<- read.csv
head(mxl)

table(mxl$genotype..forward.strand.)

calculate as a %

(table(mxl$genotype..forward.strand.)/nrow(mxl)*100)


look at an individual
install.packages("seqinr")
"gtools"

Quiality scores in FASTQ files
library(sq)
library(gtools)
s2c("DDDDDDCDDDBDDC@")
asc(s2c(____))-33


read RNA-Seq data with genotype information results table


```{r}
expr <- read.table("rs8067378_ENSG00000172057.6.txt")

head(expr)

```



```{r}
summary(expr)
```

onyl G/G 


```{r}
inds <- expr$geno== "G/G"
expr[inds,]
```




```{r}
inds <- expr$geno== "G/G"
summary(expr[inds, "exp"])
```

```{r}
inds <- expr$geno== "A/G"
summary(expr[inds, "exp"])
```

```{r}
inds <- expr$geno== "A/A"
summary(expr[inds, "exp"])
```




```{r}
boxplot(exp~geno, data=expr)
```




#significant differnces  does affect expression values 