---
title: "class_06"
author: "Robertha Amezola"
date: "May 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#lecture 6 hands-on R-Funtions 
 
#Fix version
```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
 return(answer)
}
```



```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 return(answer)
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
 return(answer)
}
```

```{r}
plot(1:10, typ="l", col="blue")
```

```{r}
read.table("test1.txt", header = TRUE, sep=",")
```

```{r}
read.csv("test1.txt")
```
```{r}
read.table("test2.txt", header = TRUE, sep="$")
```
```{r}
read.table("test3.txt")
```

Functions

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

```{r}
add (x=c(1,2,3, y=4))
```
```{r}
rescale <- function(x) {
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

# Test on a small example where you know the answer
```{r}
rescale(1:10)
```


# How would you get your function to work here…

```{r}
rescale( c(1,2,NA,3,10) )
```

```{r}
x <-  c(1,2,NA,3,10)
rng <- range(x, na.rm = TRUE)
rng
(x - rng[1]) / (rng[2] - rng[1])
```
```{r}
rescale2 <- function(x, na.rm=TRUE) {
  
  if(!is.numeric(x)) {
    stop("You need to give only numbers please")
    
  }
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```


```{r}
#rescale2(c(1,10,"string"))
```


```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 
 print("is it me you are looking for?")
 
 if(plot) {
    plot(answer, typ="b", lwd=4)
    print("Please don't sing again")
 }
 
 print("I can see it in ...")
 return(answer)
}
```



```{r}
rescale3( c(1,3,NA,10), plot = TRUE)
```


```{r}
x <- c(1,10,"string")
is.numeric(x)
#range(x, na.rm = )
```

```{r}
plot(1:10, typ="l", col="blue")
```

```{r}
read.table("test1.txt", header = TRUE, sep=",")
```

```{r}
read.csv("test1.txt")
```
```{r}
read.table("test2.txt", header = TRUE, sep="$")
```
```{r}
read.table("test3.txt")
```

Functions

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

```{r}
add (x=c(1,2,3, y=4))
```
```{r}
rescale <- function(x) {
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

# Test on a small example where you know the answer
```{r}
rescale(1:10)
```


# How would you get your function to work here…

```{r}
rescale( c(1,2,NA,3,10) )
```

```{r}
x <-  c(1,2,NA,3,10)
rng <- range(x, na.rm = TRUE)
rng
(x - rng[1]) / (rng[2] - rng[1])
```
```{r}
rescale2 <- function(x, na.rm=TRUE) {
  
  if(!is.numeric(x)) {
    stop("You need to give only numbers please")
    
  }
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```


```{r}
#rescale2(c(1,10,"string"))
```


```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 
 print("is it me you are looking for?")
 
 if(plot) {
    plot(answer, typ="b", lwd=4)
    print("Please don't sing again")
 }
 
 print("I can see it in ...")
 return(answer)
}
```



```{r}
rescale3( c(1,3,NA,10), plot = TRUE)
```


```{r}
x <- c(1,10,"string")
is.numeric(x)
#range(x, na.rm = )
```


#HW Q6


{ 
  library(bio3d)
  s1 <- read.pdb(w) # kinase with drug
  s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
  s1.b <- s1.chainA$atom$b                                    
  plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor") 
}


```{r}
Bfactor.residue<-function(kinase) { 
  library(bio3d)
  s1 <- read.pdb(kinase) # kinase with drug
  s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
  s1.b <- s1.chainA$atom$b                                    
  plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor") 
}
```
 
 #inputs of function
 (kinase)
 
 #functions and how to use it
 read.pdb-read a portein data bank coordinate file
 trim.pdb- to make a new smaller PDB obeject that has a subset of atoms from a given largr PDB object
 $__$ this is not a function but a command to that allows you to choose what data to use from over all data
 
 
#out puts of Bfactor.residue function
#change name of each kinase in order to get plots Bfactor x Residue
```{r}
Bfactor.residue("4AKE")
Bfactor.residue("1AKE")
Bfactor.residue("1E4Y")
```
