---
title: "class07_423"
author: "Robertha Amezola"
date: "April 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions revisted
we will use a file from last class
```{r}
source("http://tinyurl.com/rescale-R")
```

Try out the last day's resclae() function

```{r}
rescale(1:10)
```


Try the rescale2() function that catches string inputs- should get error

##```{r}
rescale(c(1:10, "string"))
```

##```{r}
rescale2(c(1:10, "string"))
```
should get error mistake

#Find missing NA 

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```


```{r}
is.na(x)
```

# telling me where there is NA in x

```{r}
is.na(y)
```
# TRUE where y is [NA]


#now got answer for each vector
#combining together with an AND

```{r}
is.na(x) & is.na(y)
```
#TRUE is the position NA for both vectors x and y


#how many TRUE in both (NA values) in x & y ? use the sum() function


```{r}
sum(is.na(x) & is.na(y))
```

#answer is 1

#Write this as a function
#body is the snippet

```{r}
both_na <- function(x,y) {
 sum(is.na(x) & is.na(y))  
}
```


```{r}
both_na(x,y)
```

```{r}
both_na(x, c(NA ,3 ,NA ,2 , NA))
```
 # plugged in different inputs

test, tet, test

```{r}
x <- c(NA, NA, NA)
y1 <- c( 1, NA, NA)
y2 <- c( 1, NA, NA, NA)
```


```{r}
both_na(x,y2)
```
 #What happen? we were expecting 2 so?
 
```{r}
y3 <- c(1, NA, NA,NA, NA,NA,NA)
both_na(x, y3)
```
 
 #now we got 6 what happen? takes the missing part on x to match y2 then makes it a number (recycles) to make it the same lenght


 
```{r}
3==3
```
 
```{r}
3>2
```
```{r}
3<2
```
```{r}
3!=2
```
##```{r}
lenght(y2)
```

Now lets try the both_na2() function on different lenght input vector

##```{r}
both_na2(x,y2)
```
#should get an error messege


```{r}
x
```
```{r}
which(c(F, F,T,F))
```
 #which ( is.na(c( 1, 3,NA,4)))


```{r}
which ( c( FALSE, FALSE,TRUE,FALSE, FALSE))
```

```{r}
x <-c(1,2,NA,3,NA)
y<- c(NA, 3, NA, 3 ,4)
both_na3(x,y)
```
## Internsect function

```{r}
df1
```

```{r}
df2
```

##simplify to vectors 

```{r}
x<- df1$IDs
y<- df2$IDs


x
y
```

#Next-function intersection of two vectors

```{r}
intersect(x, y)
```

```{r}
x %in% y
```

```{r}
which(x %in% y)
```

```{r}

```

```{r}
(x %in% y)
```

##working snippet combine cbind()

```{r}
cbind( x[x %in% y],
       y[y %in% x])
```

#highlight function (snippet) then click code -> extract function= named function gene_intersect
```{r}
gene_intersect <- function(x, y) {
  cbind( x[x %in% y],
         y[y %in% x])
}
```



```{r}
gene_intersect(df1$IDs, df2$IDs)
```
```{r}
gene_intersect2(df1,df2)
```

# Next step: Add df1[,gene.colname] etc to function.

```{r}
gene_intersect3(df1, df2)
```

# Additional features we could add
# - Catch and stop when user inputs weird things
# - Use different colnames for matching in df1 and df2,
# - Match based on the content of multiple columns,
# - Optionally return rows not in df1 or not in df2 with NAs
# - Optionally sort results by matching column

```{r}
merge(df1,df2, by= "IDs")
```

#sample calculate the mean of the students grades 
c(100,100,100,100,100,100,100,90)
c(100,90,90,90,90,90,97,80)

#naming
studnet1 <-c(100,100,100,100,100,100,100,90)
student2 <-cc(100,100,100,100,100,100,100,90)

```{r}
s1 <-c(100,100,100,100,100,100,100,90)
s2 <-c(100,100,100,100,100,100,100,90)
```
 #calculate the average grade dropping the lowest

```{r}
min(s1)
```
```{r}
(sum(s1)-min(s1))/7
```

```{r}
(sum(s1)-min(s1))/(length(s1)-1)
```
#made a function using s1 results
```{r}
grade <- function (s1) {
(sum(s1)-min(s1))/(length(s1)-1)
}
```


#student 2 (s2)
```{r}
grade(s2)
```

